Pillar 2 - Topic Modeling

### 2019-01-09 Pillar 2 - Topic Modeling.Rmd
Loading datasets created in the file Data Preparation
Writing function that generates a word cloud

>>>>

# Setup
```{r}
load("data_pillar_2.RDATA")
```

# TF-IDF
# TF-IDF
```{r function make_barplot and make_WC, out.height=8, out.width=16}
make_barplot <- function(data, facet, n_col = 5){

  facet <- enquo(facet)

  g <- data %>%
    rename(facet = !!facet) %>%
    ggplot(aes(reorder_within(word, tf_idf, facet), tf_idf)) +
    geom_col(show.legend = F) +
    labs(x = NULL, y = "tf-idf") +
    scale_x_reordered() +
    facet_wrap(~ facet, scales = "free", ncol = n_col) +
    coord_flip()

  ggsave(paste(facet[2], "_BP.jpeg", sep = ""), path = "Plots")
  return(g)

}

make_WC <- function(data, facet, n_col = 5){

  facet <- enquo(facet)

  g <- data %>%
    rename(facet = !!facet) %>%
    group_by(facet) %>%
    mutate(freq = tf_idf / sum(tf_idf)) %>% # normalization within clusters
    ungroup() %>%
    mutate(angle = 10 * sample(-2:2, n(), replace = T, prob = c(1,1,4,1,1))) %>%

    ggplot(aes(size = freq^0.7, label = word, 
               angle = angle, color = freq^0.7)) +
    geom_text_wordcloud_area(area_corr_power = 1,
                             eccentricity    = 1,
                             rm_outside      = T) +
    scale_radius(range = c(2, 10), limits = c(0, NA)) +
    scale_color_gradient(low = "red", high = "blue") +
    facet_wrap(~ facet, ncol = n_col) + 
      theme(
        strip.text.x     = element_text(),
        panel.background = element_rect(fill = "white"),
        plot.title       = element_text(hjust=0.5)
      )

  ggsave(paste(facet[2], "_WC.jpeg", sep = ""), path = "Plots")
  return(g)
}
```
